Consistent Polyhedral Surrogates via Embedding

### 2019-07-29 notes/top-k.tex
Added justification for restrictions back in.

@@

First, observe that we can re-write
\begin{align*} 
L^{top-k}(u)_y&=\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+\\ 
&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+
\end{align*}

One can verify that, given our assumptions on $u$, the term inside $(\cdot)_+$ of $L^{top-k}(u)_y$ is nonnegative, so we can drop the $(\cdot)_+$ operator on this report space.

>>>>

To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i \; \forall i \neq y$. 
\begin{align*}
L^{top-k}(u)_y &= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} + \epsilon\right) \right)_+\\ 
&= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} + \epsilon\right) \right)_+\\
&= \left(-\bar u_{-y} - \epsilon + \bar u_{-y} + \frac \epsilon k \right)_+ \\
&= (-\frac{k-1}{k}\epsilon)_+\\
&= 0
\end{align*}
\begin{align*}
L^{top-k}(u')_y &= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} \right) \right)_+\\ 
&= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} \right) \right)_+\\
&= \left(-\bar u_{-y} + \bar u_{-y}\right)_+ \\
&= 0
\end{align*}

Now, for any outcome $i \neq y$, we know that $\bar u_{-i} > \bar u_{-i}$ because of $u_y$.
Since $u_y$ is only added in $L^{top-k}(\cdot)_i$ as part of the $\bar u_{-i}$ term, we can see that $L^{top-k}(u)_i \geq L^{top-k}(u')_i$ for all $i \neq y$.

@@

First, observe that we can re-write
\begin{align*} 
L^{top-k}(u)_y&=\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+\\ 
&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
&=\left(1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - \min(u_y, 1)\Ind{y \leq k})_{i} \right)_+
\end{align*}
\jessie{Do we need the indicator given the assumptions...?}

Consider that the loss value is $1 + \bar u$ if $y > k$, since $u_y = 0$ in this case, so the loss is nonnegative even before applying the $(\cdot)_+$ operator.
If $y \leq k$ and $u_y \in [0,1]$, then the loss is nonnegative before applying $(\cdot)_+$ as $1-u_y \geq 0$, as is $\bar u$.
Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside $(\cdot)_+$ of $L^{top-k}(u)_y$ is equal to $\frac{1}{k-1} + 1 +  \ubar_{-y} - u_y $
Since $u_y \leq 1 +  \ubar_{-y}$, we can see this term is nonnegative.
Therefore, we can drop the $(\cdot)_+$ operator on this report space.
